### 2015-01-23 publishing/plos_template.tex
worked on intro

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
It is not unusual for labs to make ten microfluidic devices to guarnantee one will work properly.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
3D printing also allows integration of complex geometeries not possible with planar lithograpy, such as hose barbs and leur fittings.
Dissemination and distributed production is also vastly simplified due to easy shareing the design as a CAD file.
Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (Poland guy?, UK guy?) 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
\bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer. Also a bit on negative pressure Vs. positive pressure.}
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubators's condition.

>>>>

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
It is not unusual for labs to make ten microfluidic devices to guarnantee one will work properly.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
3D printing also allows integration of complex geometeries not possible with planar lithograpy, such as hose barbs and leur fittings.
Dissemination and distributed production is also vastly simplified due to easy shareing the design as a CAD file.
Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (Poland guy?, UK guy?) 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
Microfluidic cell culture devices are often made out of gas periable PDMS via soft photo lithography.
PDMS is a convient material for cell studies due to it's biocompatability, optical properties, and gas periability, faciliataing oxygen control of cell environments.
Oxygen control in cells studies is often overlooked by researchers, but important for mimicing conditions expericend by cells in vivo.

Oxygen control mulitwell inserts have been previously developed cast entirely from PDMS for 6 well culture plates. \cite{Oppegard2009, Oppegard2010}.
For a similar design to be scaled scaled (replicated) to a 24-well plate the fabriation becomes to tedious and error prone to be done by hand.
Moveing to 3D printing for the fabrication allowed futher features to be incoporated such as integrated distubtion channels and hose barbs, while elminating fabrication time and yeild.
Although avalible 3D pritable materials are non-gas-permiable, the addition of a PDMS membrane allows gas transfer. 
The previous 6-well PDMS device featured paralene coating to eliminate exchange of gas in th PDMS bulk. 
\bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer. Also a bit on negative pressure Vs. positive pressure. - I don't have any data or any reason that I can prove for doing this. I was orginally afraid that the membranes would come off from the pressure.
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubators's condition.
